Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-11-18 manuscript/manuscript.tex
add data citation
comment out inline figures

All code for data processing, model fitting, and model evaluation is available at Stachelek et al. (2023a) the pipeline for which is shown in Figure 1. All data used in the study are available in Stachelek et al. (2023b).

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/data-processing_model-architecture}
          \caption{Diagram of the data processing, model fitting, tuning, and prediction pipeline.}
    \end{center}    
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_validation}
          \caption{Out of sample test set performance for salinity, turbidity, and temperature models respectively. Hatching indicates the location of 80\% of the data points.}
    \end{center}    
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.8\textwidth,keepaspectratio]{figures/_importance_all}
          \caption{Random Forest importance plot for salinity, temperature, and turbidity models. Note that all features may not be present in all models if they were dropped as a result of recursive feature elimination.}
    \end{center}    
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.7\textwidth,keepaspectratio]{figures/_seasonality}
          \caption{Seasonal Random Forest prediction results for temperature and salinity.}
    \end{center}    
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_rf-vs-cbofs}
          \caption{Comparison between Random Forest salinity prediction results and a CBOFS snapshot for Sept, 4, 2022.}
    \end{center}    
\end{figure}

>>>>

All code for data processing, model fitting, and model evaluation is available at Stachelek et al. (2023a) the pipeline for which is shown in Figure 1. All data used in the study are available in \cite{stachelekjemmachesapeake}.

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/data-processing_model-architecture}
%           \caption{Diagram of the data processing, model fitting, tuning, and prediction pipeline.}
%     \end{center}    
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_validation}
%           \caption{Out of sample test set performance for salinity, turbidity, and temperature models respectively. Hatching indicates the location of 80\% of the data points.}
%     \end{center}
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.8\textwidth,keepaspectratio]{figures/_importance_all}
%           \caption{Random Forest importance plot for salinity, temperature, and turbidity models. Note that all features may not be present in all models if they were dropped as a result of recursive feature elimination.}
%     \end{center}    
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.7\textwidth,keepaspectratio]{figures/_seasonality}
%           \caption{Seasonal Random Forest prediction results for temperature and salinity.}
%     \end{center}    
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_rf-vs-cbofs}
%           \caption{Comparison between Random Forest salinity prediction results and a CBOFS snapshot for Sept, 4, 2022.}
%     \end{center}    
% \end{figure}
